Testing gene methylation enrichment analysis approaches using simulated data - summarise data

### 2023-12-31 figs/GSE158422_simulate_summary.Rmd
lrm

5. ALT: alcres

6. ALW: nalcres

7. ALM: almres

@@

l1 <- list("GSA"=gres2,"LAT"=lacres2,"LTT"=lactopres2,"LAW"=nlacres2,
  "LAM"=lacmres2,"ALT"=alcres2,"ALW"=nalcres2,"ALM"=almres2)

@@

l2 <- list("GSA"=gres2,"LAT"=lacres2,"LTT"=lactopres2,"LAW"=nlacres2,
  "LAM"=lacmres2,"ALT"=alcres2,"ALW"=nalcres2,"ALM"=almres2)

@@

l3 <- list("GSA"=gres2,"LAT"=lacres2,"LTT"=lactopres2,"LAW"=nlacres2,
  "LAM"=lacmres2,"ALT"=alcres2,"ALW"=nalcres2,"ALM"=almres2)

>>>>

5. LRM: lrmres

6. ALT: alcres

7. ALW: nalcres

8. ALM: almres

@@

l1 <- list("GSA"=gres2,"LAT"=lacres2,"LTT"=lactopres2,"LAW"=nlacres2,
  "LAM"=lacmres2, "LRM"=lrmres2, "ALT"=alcres2,"ALW"=nalcres2,"ALM"=almres2)

@@

l2 <- list("GSA"=gres2,"LAT"=lacres2,"LTT"=lactopres2,"LAW"=nlacres2,
  "LAM"=lacmres2, "LRM"=lrmres2, "ALT"=alcres2,"ALW"=nalcres2,"ALM"=almres2)

@@

l3 <- list("GSA"=gres2,"LAT"=lacres2,"LTT"=lactopres2,"LAW"=nlacres2,
  "LAM"=lacmres2, "LRM"=lrmres2, "ALT"=alcres2,"ALW"=nalcres2,"ALM"=almres2)
